Introductory statistics with `intRo`

### 2016-02-18 jcgs-paper-2016/paper.Rmd
Typo typo

The widespread adoption of \texttt{R} as a tool for statistical analysis has undoubtedly been an important development for the scientific community. However, using \texttt{R} in most cases still requires a basic knowledge of programming concepts which may pose a steep learning curve for the introductory statistics student. This additional time commitment may explain why introductory courses often utilize software applications such as \texttt{JMP}, even though instructors tend to use a tool like \texttt{R} in their own work. This brings along signficant compromises must be made when using software like \texttt{JMP}, including dealing with software licenses and unsupported desktop platforms.

@@

Upon the release of \texttt{RStudio}'s \texttt{Shiny} [@shiny] it became easier for an R-based analysis to be converted to an interactive web application. This in turn led us to create an introductory statistics application which we call \texttt{intRo}, available at http://www.intro-stats.com. \texttt{intRo} offers a number of key advantages over traditional statistics software, including ease of use and an aim to foster student interest. Additionally, \texttt{intRo} stands apart from new tools in that it is a supplement to an existing class, fully usable by a beginning statistics student. These advantages will be discussed at length in this text.

>>>>

The widespread adoption of \texttt{R} as a tool for statistical analysis has undoubtedly been an important development for the scientific community. However, using \texttt{R} in most cases still requires a basic knowledge of programming concepts which may pose a steep learning curve for the introductory statistics student. This additional time commitment may explain why introductory courses often utilize software applications such as \texttt{JMP}, even though instructors tend to use a tool like \texttt{R} in their own work. Still, some compromises must be made when using software like \texttt{JMP}, including dealing with software licenses and unsupported desktop platforms.

@@

Upon the release of \texttt{RStudio}'s \texttt{Shiny} [@shiny] it became easier for an R-based analysis to be converted to an interactive web application. This in turn led us to create an introductory statistics application which we call \texttt{intRo}, available at http://www.intro-stats.com. \texttt{intRo} offers a number of key advantages over traditional statistics software, including ease of use and an aim to foster student interest in coding. Additionally, \texttt{intRo} stands apart from new tools in that it is a supplement to an existing class, fully usable by a beginning statistics student. These advantages will be discussed at length in this text.
